AppPAL for Android

### 2015-10-01 paper.tex
updates

\begin{abstract}
  It can be difficult to find mobile apps that respect your security and privacy.
  At work, employers rely on employees enforcing company policies about apps at the workplace correctly.
  Users must judge apps by the information shown to them by the store.
  Only 17\% of users pay attention to an apps permissions during installation~\cite{Felt:2012hm} and
  most users do not understand how permissions relate to the capabilities of an app~\cite{Kelley:2012bw}.
  We present AppPAL: a policy language for Android to describe app installation  policies.
  AppPAL goes beyond existing policy enforcement tools, such as Kirin~\cite{Enck:2008vn}, adding delegation relationships and the connecting to static analysis tools.
  We use AppPAL to explore what kinds of policies users use when installing apps, demonstrating the privacy paradox when comparing user's privacy views to their actual behaviour.
\end{abstract}

@@

We present AppPAL, an instantiation of Becker~\etal's SecPAL~\cite{Becker:2006vh} with constraints\footnote{A constraint makes use of information checkable using information external to the language, such as the time of day or output of a static analysis tool} and predicates that allow us to decide which apps to run or install.
The language allows us to reason about apps using statements from third parties.
The implementation allows us to enforce the policies on a device.
We can express trust relationships amongst these parties; use constraints to do additional checks, such as using static analysis results.
This lets us enforce more complex policies than existing tools such as Kirin~\cite{Enck:2009ko} which are limited to permissions checks.

@@

We can delegate policy specification to third parties or roles, and assign principals to roles:
\begin{lstlisting}
"alice" says "it-department" can-say "work-policy" isMetBy(App).
"alice" says "alice" can-act-as "it-department".
\end{lstlisting}
We can write policies specifying which permissions an app must or must not have by its app store categorization:
\begin{lstlisting}
"alice" says App isRunnable
if "permissions-policy" isMetBy(App).
"alice" says "permissions-policy" isMetBy(App)
if App isAnApp
where
category(App, "Photography"),
hasPermission(App, "LOCATION") = false,
hasPermission(App, "CAMERA") = true.
\end{lstlisting}

There has been a great amount of work on developing app analysis tools for Android.
Tools such as Stowaway~\cite{Felt:2011kj} detect over-privileged apps.
TaintDroid~\cite{Enck:2010uw} and FlowDroid~\cite{Fritz:2013vi} can do taint and control flow analysis; sometimes even between app components.
Other tools like QUIRE~\cite{Bugiel:2012ui} can find privilege escalation attacks between entire apps.
ScanDAL~\cite{Kim:2012vt} and SCanDroid~\cite{Fuchs:2009vi} help detect privacy leaks.
Appscopy~\cite{Feng:kPGZr_ja} searches for specific kinds of malware.
Tools like DroidRanger~\cite{Zhou:2012tb} scan app markets for malicious apps.
Many others exist checking and certifying other aspects of app behaviour.

AppPAL can act as a \emph{``glue"} between static analysis tools and the app installation policies device owner's are trying to enforce.
For example a user might not want to install apps with SSL errors (which Mallodroid can check for~\citep{Fahl:2012dj}) or malicious apps as determined by their anti-virus.
Using AppPAL we can combine tools for checking apps to implement the user's policies.
\begin{lstlisting}
"alice" says App isInstallable
  if App isAnApp
  where mallodroidCheck(App) = true,
        avCheck(App) = true.
\end{lstlisting}

@@

An employee \emph{Alice} works for her employer \emph{Emma}.
Emma allows Alice to use her personal phone as a work phone but has some specific concerns.
\begin{itemize}
  \item Alice shouldn't run any apps that can track her movements.
    The testing labs are at a secret location and it mustn't be leaked.
  \item Apps should come from a reputable source, such as the Google Play Store.
  \item Emma uses an \ac{av} program by McAfee.
    It should check all apps before they're installed.
\end{itemize}

To ensure this policy is met Alice promises to follow it.
She might even sign a document promising never to break the rules within the policy.
This is error-prone---what if she makes a mistake or misses an app that breaks her policy?
Alternately Emma's policy could be partially enforced using existing tools.
\emph{Google's Device Policy for Android}~\cite{GoogleAppsDeviceP:tz} could configure Alice's device to disallow apps from outside the Google Play Store and let Emma set the permissions granted to each app~\cite{AndroidMPermission:2015uq}.

AppPAL builds on these tools, but make the trust and delegation relationships explicit and provide a rigorous and extensible means for deciding whether an app meets a policy.
Various tools such as AppGuard~\cite{Backes:2012vm}, Dr.~Android~\&~Mr.~Hide~\cite{Jeon:2012ki} or AppFence~\cite{Hornyack:2011wq} can control the permissions or data an app can get.
These could be used to used to ensure no location data is ever obtained.
Alternately other tools like Kirin~\cite{Enck:2009ko}, Flowdroid~\cite{Fritz:2013vi} or DroidSafe~\cite{Gordon:2015et} could check that the locations are never leaked to the web.
Various anti-virus programs are available for Android---one could be installed on Alice's phone checking against McAfee's signatures.

Whilst we could implement Emma's policy using existing tools it is a clumsy solution---they are not flexible.
If Emma changes her policy or Alice changes jobs she needs to recheck her apps and then alter or remove the software on her phone to ensure compliance.
It isn't clear what an app must do to be run, or what checks have been done if it is already running on the phone.
The relationship between Alice (the user), Emma (the policy setter) and the tools Emma trusts to implement her policy isn't immediately apparent.

@@

We propose a change to the mobile ecosystem, shown in \autoref{fig:ecosystem}.
People have policies which are enforced by AppPAL on their devices.
They can be composed with policies from employers or others to create enhanced devices that ensure apps meet the policies of their owners.
The device can make use of vetting services which run tools to infer complex properties about apps.
Users can buy from enhanced stores which ensure the only apps they sell are the apps which meet the explicitly specified store policies.
Developers could decide which stores to sell their apps in on the basis of policies about stores.

@@

"emma" says
  "reputable-policy" isMetBy(App) @\label{lst:corporate_3}@
      if App isReputable.

"emma" says "google-play" can-say
  App isReputable. @\label{lst:corporate_4}@
    \end{lstlisting}
  \end{minipage}\begin{minipage}[t]{0.5\textwidth}
    \begin{lstlisting}[numbers=left,
                       escapeinside={@}{@},
                       firstnumber=15,
                       basicstyle=\scriptsize\ttfamily,
                       stringstyle=\scriptsize\sffamily,
                       keywordstyle=\scriptsize\slshape]
"emma" says "anti-virus-policy" isMetBy(App) @\label{lst:corporate_5}@
  if App isAnApp
  where
    mcAfeeVirusCheck(App) = false.

@@

"emma" says
  "no-location-permissions" isMetBy(App) @\label{lst:corporate_7}@
    if App isAnApp
    where
      hasPermission(App, "LOCATION")=false.
\end{lstlisting}
\end{minipage}
\caption{AppPAL policy implementing Emma's security requirements}
\label{lst:corporate}
\end{figure}

In \autoref{lst:corporate_1} Alice gives Emma the ability to specify whether an \code{App} (a variable) \code{isRunnable} (a predicate).
She allows her to delegate the decision further if she chooses (\code{can-say inf}).
Next in \autoref{lst:corporate_2} Emma specifies her concerns as policies to be met (the \code{isMetBy()} predicate that takes an app as its argument).
If Emma can be convinced all these policies are met then she will say the \code{App isRunnable}.
In \autoref{lst:corporate_3} and \autoref{lst:corporate_4} Emma specifies that an app meets the \code{reputable-policy} if the \code{App isReputable};
  with \code{"google-play"} specified as the decider of what is buyable or not.
This time Google is not allowed to delegate the decision further (\code{can-say}).
In other words Google is not allowed to specify Amazon as a supplier of apps as well.
Google must say what is buyable directly for Emma to accept it.
Emma specifies the \code{"anti-virus-policy"} in \autoref{lst:corporate_5}.
Here we use a constraint.
When checking the policy the \code{mcAfeeVirusCheck} should be run on the \code{App}.
Only if this returns \code{false} will the policy be met.
To specify the \code{"no-tracking-policy"} Emma says that the \code{"no-location-permissions"} rules implement the \code{"no-tracking-policy"} (\autoref{lst:corporate_6}).
Emma specifies this in \autoref{lst:corporate_7} by checking the app is missing two permissions.

@@

In this scenario we have imagined Alice wanting to check the apps as she installs them.
We could also imagine Emma wanting a personalised app store where all apps sold meet her policy.
With AppPAL this can be implemented by taking an existing store and selectively offering only the apps which will meet the user's policy.
This gives us a \emph{filtered store} which, from an existing set of apps, we get a personalised store that only sells apps that meet a policy.

@@

Sometimes we might want to use location data.
For instance Emma might want to check that Alice is at her office.
Emma might track Alice using a location tracking app.
Provided the app only talks to Emma, and it uses SSL correctly (which Mallodroid can check for~\cite{Fahl:2012dj}) she is happy to relax the policy.

@@

AppPAL has the same policy checking rules as SecPAL~\cite{Becker:2006vh}.
AppPAL uses an assertion context of known facts and rules
We do not use Becker~\etal's DatalogC~\cite{Li:2003ix}~based checking algorithm, as no DatalogC library exists for Android.
We have implemented the rules directly in Java.
Pseudo-code is given in \autoref{fig:pseudocode}.

Like Becker~\etal~we make use of an assertion context to store known statements and rules, as well as facts that are deduced during checking.
On a mobile device memory is at a premium.
We would like to keep the assertion context as small as possible.
For some assertions (like \code{isAnApp}) we derive them by checking the arguments at evaluation time.
This gives us greater control of the evaluation and how the assertion context is created.
For example, when checking the \code{isAnApp} predicate;
  we can fetch the assertion that the subject is an app based on the app in question.

@@

Lin~\etal~identified four types of user.
The \emph{Conservative} (C) users were uncomfortable allowing an app access to any personal data for any reason.
The \emph{Unconcerned} (U) users felt okay allowing access to most data for almost any reason.
The \emph{Advanced} (A) users were comfortable allowing apps access to location data but not if it was for advertising reasons.
Opinions in the largest cluster, \emph{Fencesitters} (F), varied but were broadly against collection of personal data for advertising purposes.
We wrote AppPAL policies to describe each of these behaviours as increasing sets of permissions.
These simplify the privacy policies identified as by Lin~\etal~as we do not take into account the reason each app might have been collecting each permission.

@@

\begin{figure}\centering
  \subfigure[Advanced and non-\ac{pup} policies.]{%
    \includegraphics[width=0.48\linewidth]{./figures/advanced-v-pup.eps}
    \label{fig:versus_pup}}
    \subfigure[Advanced and Mallodroid policies.]{%
    \includegraphics[width=0.48\linewidth]{./figures/advanced-v-mallodroid_m.eps}
    \label{fig:versus_mallodroid}}
  \caption{Compliance with the advanced policy and the non-\ac{pup} and SSL policies.}
  \label{fig:versus}
\end{figure}

@@

The \emph{MalloDroid} tool~\citep{Fahl:2012dj} can scan apps for SSL misconfigurations.
SSL misconfigurations are dangerous as they can undermine any privacy guarantees that SSL/TLS usage gives.
We set up AppPAL to use Mallodroid results as a constraint and measured the percentage of apps each user had installed that did not have issues or suspected issues when scanned with Mallodroid.
Users who were complying with the advanced policy were no better at avoiding apps with SSL errors than any other users (Figure~\autoref{fig:versus_mallodroid}).

@@

We have presented AppPAL: an authorization logic for describing app installation policies primarily designed to help achieve security and privacy objectives but which can also \emph{lock down} devices in other ways.
We have shown how the language can be used to describe an app installation policy;
  and given brief descriptions of how other policies might be described.
Using app installation data and user privacy policies expressed using AppPAL we showed how the privacy paradox can be seen in the Android ecosystem.
This motivates the need for tools

Further work is required to tightly integrate AppPAL into Android.
One way to integrate AppPAL on Android would be as a \emph{required checker}: a program that checks all apps before installation.
Google uses the required checker API to check for known malware and jailbreak apps.
We would use AppPAL to check apps meet policies before installation.
Unfortunately the API is protected and it would require the phone to be rooted.
Alternatively, AppPAL could be integrated as a service to reconfigure app permissions.
Android Marshmallow has an iOS like permissions model where permissions can be granted and revoked at any time.
These will be manually configurable by the user through the settings app.
We can imagine AppPAL working to reconfigure these settings (and set their initial grant or deny states) based on a user's policy, as well as the time of day or the user's location.
A policy could deny notifications while a user is driving, for example, by checking if they are using Android Auto~\cite{AndroidAuto:uw} (an app to interact with a car's center console) or moving along a road at high speed.

>>>>

\begin{abstract}
  It can be difficult to find mobile apps that respect your security and privacy.
  Employers rely on employees enforcing company policies about apps at the workplace correctly.
  Users must judge apps by the information shown to them by the store.
  Only 17\% of users pay attention to an apps permissions during installation~\cite{Felt:2012hm} and
  most users do not understand how permissions relate to the capabilities of an app~\cite{Kelley:2012bw}.
  We present AppPAL: a policy language for Android to describe app installation  policies.
  AppPAL goes beyond existing policy enforcement tools, like Kirin~\cite{Enck:2008vn}, adding delegation relationships and the connecting to static analysis tools.
  We use AppPAL to explore what kinds of policies are used when installing apps, demonstrating the privacy paradox when comparing user's privacy views to their actual behaviour.
\end{abstract}

@@

We present AppPAL, an instantiation of Becker~\etal's SecPAL~\cite{Becker:2006vh} with constraints\footnote{A constraint makes use of information checkable using information external to the language, such as the time of day or output of a static analysis tool.} and predicates that allow us to decide which apps to run or install.
The language allows us to reason about apps using statements from third parties.
The implementation allows us to enforce the policies on a device.
We can express trust relationships amongst these parties; use constraints to do additional checks, such as using static analysis results.
This lets us enforce more complex policies than existing tools such as Kirin~\cite{Enck:2009ko} which are limited to permissions checks.

@@

We can delegate policy specification to third parties or roles, and assign principals to roles:
\begin{lstlisting}
"alice" says "it-department" can-say "work-policy" isMetBy(App).
"alice" says "alice" can-act-as "it-department".
\end{lstlisting}
We can write policies specifying which permissions an app must or must not have by its app store categorization.
For example it would be okay allowing a photography app access to the camera, but not to the location data if the user doesn't want their photos geotagged.
\begin{lstlisting}
"alice" says App isRunnable
  if "permissions-policy" isMetBy(App).
"alice" says "permissions-policy" isMetBy(App)
  if App isAnApp
  where
    category(App, "Photography"),
    hasPermission(App, "LOCATION") = false,
    hasPermission(App, "CAMERA") = true.
\end{lstlisting}

There has been a great amount of work on developing app analysis tools for Android.
Tools such as Stowaway~\cite{Felt:2011kj} detect over-privileged apps.
TaintDroid~\cite{Enck:2010uw} and FlowDroid~\cite{Fritz:2013vi} can do taint and control flow analysis; sometimes even between app components.
Other tools like QUIRE~\cite{Bugiel:2012ui} can find privilege escalation attacks between entire apps.
ScanDAL~\cite{Kim:2012vt} and SCanDroid~\cite{Fuchs:2009vi} help detect privacy leaks.
Appscopy~\cite{Feng:kPGZr_ja} searches for specific kinds of malware.
Tools like DroidRanger~\cite{Zhou:2012tb} scan app markets for malicious apps.
Various tools such as AppGuard~\cite{Backes:2012vm}, Dr.~Android~\&~Mr.~Hide~\cite{Jeon:2012ki} or AppFence~\cite{Hornyack:2011wq} can control the permissions or data an app can get.
MalloDroid~\citep{Fahl:2012dj} looks for apps configured to use SSL incorrectly (for instance by not verifying hostnames or certificates).
Many others exist checking and certifying other aspects of app behaviour.

AppPAL can act as a \emph{``glue"} between static analysis tools and the app installation policies device owner's are trying to enforce.
This avoids creating tools with hard-coded fixed policies
For example a store might not want to sell apps with SSL errors or malicious apps as determined by their anti-virus.
Using AppPAL we can combine tools for checking apps to implement the store's policies.
\begin{lstlisting}
"play-store" says App isInstallable
  if App isAnApp
  where mallodroidCheck(App) = true,
         mcafeeAVCheck(App) = true.
\end{lstlisting}

@@

An employee \emph{Alice} works for \emph{Emma}.
Emma allows Alice to use her personal phone as a work phone but has some specific concerns.
\begin{itemize}
  \item Alice shouldn't run any apps that can track her movements.
    Alice's workplace is at a secret location and it mustn't be leaked.
  \item Apps should come from a reputable source, such as the Google Play Store.
  \item Emma uses an \ac{av} program by McAfee.
    It should check all apps before they're installed.
\end{itemize}

To ensure this policy is met Alice promises to follow it.
She might even sign a document promising never to break the rules within the policy.
This is error-prone---what if she makes a mistake or misses an app that breaks her policy
Alternately Emma's policy could be partially enforced using existing tools.
\emph{Google's Device Policy for Android}~\cite{GoogleAppsDeviceP:tz} could configure Alice's device to disallow apps from outside the Google Play Store and let Emma set the permissions granted to each app~\cite{AndroidMPermission:2015uq}.

We could implement Emma's policy using existing tools (such as an AV checker, and a taint analysis tool like Flowdroid~\cite{Fritz:2013vi}) but it is a clumsy solution---they are not flexible.
Each has to be configured separately to implement only part of the policy.
If Emma changes her policy or Alice changes jobs she needs to recheck her apps and then alter or remove the software on her phone to ensure compliance.
It isn't clear what an app must do to be run, or what checks have been done if it is already running on the phone.
The relationship between Alice (the user), Emma (the policy setter) and the tools Emma trusts to implement her policy isn't immediately apparent.

@@

We propose a change to the mobile ecosystem shown in \autoref{fig:ecosystem}.
People have policies which are enforced by AppPAL on their devices.
They can be composed with policies from employers or others to create enhanced devices that ensure apps meet the policies of their owners.
The device can make use of vetting services which run tools to infer complex properties about apps.
Users can buy from enhanced stores which ensure the only apps they sell are the apps which meet the explicitly specified store policies.
Developers could decide which stores to sell their apps in on the basis of policies about stores.

@@

"emma" says
  "reputable-policy" isMetBy(App) @\label{lst:corporate_3}@
      if App isBuyable.

"emma" says "google-play" can-say
  App isBuyable. @\label{lst:corporate_4}@
    \end{lstlisting}
  \end{minipage}\begin{minipage}[t]{0.5\textwidth}
    \begin{lstlisting}[numbers=left,
                       escapeinside={@}{@},
                       firstnumber=15,
                       basicstyle=\scriptsize\ttfamily,
                       stringstyle=\scriptsize\sffamily,
                       keywordstyle=\scriptsize\slshape]
"emma" says "anti-virus-policy" isMetBy(App) @\label{lst:corporate_5}@
  if App isAnApp
  where
    mcAfeeVirusCheck(App) = false.

@@

"emma" says
  "no-location-permissions" isMetBy(App) @\label{lst:corporate_7}@
    if App isAnApp
    where
      hasPermission(App, "LOCATION")=false.
\end{lstlisting}
\end{minipage}
\caption{AppPAL policy implementing Emma's security requirements.}
\label{lst:corporate}
\end{figure}

In \autoref{lst:corporate_1} Alice gives Emma the ability to specify whether an \code{App} (a variable) \code{isRunnable} (a predicate).
She allows her to delegate the decision further if she chooses (\code{can-say inf}).
Next in \autoref{lst:corporate_2} Emma specifies her concerns as policies to be met (the \code{isMetBy()} predicate that takes an app as its argument).
If Emma can be convinced all these policies are met then she will say the \code{App isRunnable}.
In \autoref{lst:corporate_3} and \autoref{lst:corporate_4} Emma specifies that an app meets the \code{reputable-policy} if the \code{App isBuyable};
  with \code{"google-play"} specified as the decider of what is buyable or not.
Google is not allowed to delegate the decision further (\code{can-say} as oposed to \code{can-say inf}).
In other words Google is not allowed to specify Amazon as a supplier of apps as well.
Google must say what is buyable directly for Emma to accept it.
Emma specifies the \code{"anti-virus-policy"} in \autoref{lst:corporate_5}.
Here we use a constraint.
When checking the policy the \code{mcAfeeVirusCheck} should be run on the \code{App}.
Only if this returns \code{false} will the policy be met.
To specify the \code{"no-tracking-policy"} Emma says that the \code{"no-location-permissions"} rules implement the \code{"no-tracking-policy"} (\autoref{lst:corporate_6}).
Emma specifies this in \autoref{lst:corporate_7} by checking the app is missing two permissions.

@@

We could also imagine Emma wanting a personalised app store where all apps sold meet her policy.
With AppPAL this can be implemented by taking an existing store and selectively offering only the apps which will meet the user's policy.
This gives us a \emph{filtered store} which, from an existing set of apps, we get a personalised store that only sells apps that meet a policy.

@@

Sometimes we might want to use location data.
For instance Emma might want to check that Alice is at her office.
Emma might track Alice using a location tracking app.
Provided the app only talks to Emma, and it uses SSL correctly (using MalloDroid~\cite{Fahl:2012dj}) she is happy to relax the policy.

@@

AppPAL has the same policy checking rules as SecPAL~\cite{Becker:2006vh}.
AppPAL uses an assertion context of known facts and rules, as well as facts deduced while checking.
We do not use Becker~\etal's DatalogC based checking algorithm, as no DatalogC library exists for Android.
We have implemented the rules directly in Java.
Pseudo-code is given in \autoref{fig:pseudocode}.

On a mobile device memory is at a premium.
We would like to keep the assertion context as small as possible.
For some assertions (like \code{isAnApp}) we derive them by checking the arguments at evaluation time.
This gives us greater control of the evaluation and how the assertion context is created.
For example, when checking the \code{isAnApp} predicate;
  we can fetch the assertion that the subject is an app based on the app in question.

@@

Lin~\etal~identified four types of user.
The \emph{Conservative} (C) users were uncomfortable allowing an app access to any personal data for any reason.
The \emph{Unconcerned} (U) users felt okay allowing access to most data for almost any reason.
The \emph{Advanced} (A) users were comfortable allowing apps access to location data but not if it was for advertising reasons.
Opinions in the largest cluster, \emph{Fencesitters} (F), varied but were broadly against collection of personal data for advertising purposes.
We wrote AppPAL policies to describe each of these behaviours as increasing sets of permissions.
These simplify the privacy policies identified as by Lin~\etal~as we do not take into account the reason each app might have been collecting each permission.
Using AppPAL we could write more precise rules if we could determine why each permission was requested.
Lin~\etal~used Androguard~\cite{Desnos:ub} as well as manual analysis to determine the precise reasons for each permission~\cite{Sadeh:2014vq}.

@@

\begin{figure}\centering
  \subfigure[Advanced and non-\ac{pup} policies.]{%
    \includegraphics[width=0.48\linewidth]{./figures/advanced-v-pup.eps}
    \label{fig:versus_pup}}
    \subfigure[Advanced and MalloDroid policies.]{%
    \includegraphics[width=0.48\linewidth]{./figures/advanced-v-mallodroid_m.eps}
    \label{fig:versus_mallodroid}}
  \caption{Compliance with the advanced policy and the non-\ac{pup} and SSL policies.}
  \label{fig:versus}
\end{figure}

@@

The \emph{MalloDroid} tool~\citep{Fahl:2012dj} can scan apps for SSL misconfigurations.
SSL misconfigurations are dangerous as they can undermine any privacy guarantees that SSL/TLS usage gives.
MalloDroid can scan for several different misconfigurations, and distinguishes cases where the app is definitely misconfigured from those where there is some doubt.
We set up AppPAL to use MalloDroid results as a constraint and measured the percentage of apps each user had installed that did not have issues or suspected issues when scanned with MalloDroid.
Users who were complying with the advanced policy were no better at avoiding apps with SSL errors than any other users (Figure~\autoref{fig:versus_mallodroid}).
This emphasizes that AppPAL policies are more powerful than manually picking apps as they can incorporate checks privacy aware users may want but which they cannot check for without additional tools.

@@

We have presented AppPAL: an authorization logic for describing app installation policies primarily designed to help achieve security and privacy objectives but which can also \emph{lock down} devices in other ways.
Using app installation data and user privacy policies expressed using AppPAL we showed how the privacy paradox can be seen in the Android ecosystem.
We showed how static analysis tools can be integrated into AppPAL to check for properties beyond the scope of the language and to act as a glue between different policies.

AppPAL currently runs either an Android app or a Java program.
Further work is needed to tightly integrate AppPAL into Android.
One way to integrate AppPAL on Android would be as a \emph{required checker}: a program that checks all apps before installation.
Google uses the required checker API to check for known malware and jailbreak apps.
We would use AppPAL to check apps meet policies before installation.
The API is protected, however, and it would require the phone to have a custom firmware.
This is undesirable as it would make AppPAL difficult to install for most users, and negate the other security enhancements (such as timely updates and patches) provided by the standard Android system.
Alternatively, AppPAL could be integrated as a service to reconfigure app permissions.
Android Marshmallow has an iOS like permissions model where permissions can be granted and revoked at any time.
These will be manually configurable by the user through the settings app.
We can imagine AppPAL working to reconfigure these settings (and set their initial grant or deny states) based on a user's policy, as well as the time of day or the user's location.
A policy could deny notifications while a user is driving, for example, by checking if they are using Android Auto~\cite{AndroidAuto:uw} (an app to interact with a car's center console) or moving along a road at high speed.
